Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2020-05-28 Manuscript/manuscript.Rmd
added figure 5E description to results

Next, we evaluated the biological significance of *preciseTAD* boundaries. Enriched heatmaps indicated that our predicted boundaries were more enriched for CTCF sites than either ARROWHEAD or PEAKACHU boundaries alone (Figure 5 B-C. Likewise, *preciseTAD* boundaries were also more enriched for other molecular drivers of 3D chromatin including RAD21, SMC3, and ZNF143 for both GM12878 and K562 cell lines (Supplementary Figures 8-9). Furthermore, when compared to called TAD or loop boundaries, *preciseTAD* were found to be statistically significantly closer to the same cell line-specific top ranked TFBS (Figure 5D, Supplementary Figure 10-11).

>>>>

Next, we evaluated the biological significance of *preciseTAD* boundaries. Enriched heatmaps indicated that our predicted boundaries were more enriched for CTCF sites than either ARROWHEAD or PEAKACHU boundaries alone (Figure 5 B-C. Likewise, *preciseTAD* boundaries were also more enriched for other molecular drivers of 3D chromatin including RAD21, SMC3, and ZNF143 for both GM12878 and K562 cell lines (Supplementary Figures 8-9). When compared to called TAD or loop boundaries, *preciseTAD* boundaries were found to be statistically significantly closer to the same cell line-specific top ranked TFBS (p=??? and p=??? vs ARROWHEAD and PEAKACHU respectively) (Figure 5D, Supplementary Figure 10-11). We also inspected the affect of resolution on locations of TAD boundaries specifically. We found that *preciseTAD* boundaries exhibited higher pairwise Jaccard indices between adjacent resolutions than ARROWHEAD boundaries, thus implying stronger invariance toward resolution (Figure 5E).
